### 2017-03-10 character_coding/CharacterEvolution.Rmd
added FactoMineR PCA plots

#Packages BIO-PHYLO
library('vegan')
library("ape")
library("ggtree")
library("phangorn")
library("phytools")
library("picante")
library("geiger")
library("phylobase")
library("fields")
library("adephylo")
library("geomorph")
library("phylolm")

@@

###Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=18, fig.width=18, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot
```

>>>>

#Packages BIO-PHYLO
library('vegan')
library("ape")
library("ggtree")
library("phangorn")
library("phytools")
library("picante")
library("geiger")
library("phylobase")
library("fields")
library("adephylo")
library("geomorph")
library("phylolm")
library("FactoMineR")
library("factoextra")

@@

###Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=10, fig.width=19, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot

dpruned_data[,c(13,14,15,17,18)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(13,14,15,17,18)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE

rpcaZ %>% fviz_screeplot(addlabels=T)
rpcaZ %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
rpcaZ %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

rpcaZ %>% fviz_pca_ind(repulse = T)

### 2017-03-10 manuscript.rmd
added FactoMineR PCA plots

	# Graphics
	library( cowplot )
	library( ggtree )
	library( GGally )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
	library( RGraphics )

@@

Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=18, fig.width=18, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot
```

>>>>

	# Graphics
	library( cowplot )
	library( ggtree )
	library( GGally )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
	library( RGraphics )
  library( factoextra )
  library( FactoMineR )

@@

Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=18, fig.width=18, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot

dpruned_data[,c(13,14,15,17,18)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(13,14,15,17,18)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE

rpcaZ %>% fviz_screeplot(addlabels=T)
rpcaZ %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
rpcaZ %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

rpcaZ %>% fviz_pca_ind(repulse = T)
```
